---
title: "Reproducible Pitch Presentation"
author: "Abhijeet Mohite"
date: "03/07/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Price prdeictor for diamonds

This is a price predictor for diamonds.It uses various inputs from the user to predict the price of diamonds. 


This is the link for the shiny app
https://abhijeetkmohite.shinyapps.io/Shinyapp/

This is the link for the Reproducible pitch
https://rpubs.com/abhijeetkmohite/ReproduciblePitch


## Inputs used in the app

- Carrets
- Cut
- Colour
- Clarity

Based on the above inputs the price of the diamond is predicted.

## This is the code for the diamonds dataset taken in the analysis

```{r, echo = TRUE}
library(ggplot2)
library(dplyr)
head(diamonds)
diam <- diamonds[,c(1:4,7)]

```

## This is the code for one of the plots used in the analysis

```{r,echo=TRUE}
fair_diamonds <- diamonds %>%
  filter(cut == "Fair")
ggplot(data = fair_diamonds, aes(x = price, y = carat)) +
  geom_point()
ggplot(data = fair_diamonds, aes(x = price, y = carat)) +
  geom_point(position = "jitter")

```

## Thank You
Thank You for giving your time in seeing my presentation
